### 2020-03-31 draft.tex
removed extra intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% First Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are two basic sorts of generating functions in prevalent use in
combinatorics. There are the \emph{analytic} generating functions arising from power
series
$$\sum_{n \in \Nb} a_n x^n$$
and the \emph{Dirichlet} generating functions arising from Dirichlet series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
The sequence of coefficients $a_n$ counts the amount of objects $A_n$ associated to an
$n$-element set $\underline{n} := \{0,\ldots, n-1\}$. For example, if $A_n$ is
the set of injections from $\underline{n}$ to $\underline{k}$, then $a_n = {k
  \choose n}$.

The power of the generating function formalism lies in way that algebraic and
analytic operations on the generating functions shadow combinatorial operations
on the sets that their coefficients count. This ``shadowing'' can be seen as an
instance of \emph{decategorification}. In his seminal paper \emph{Une
  th{\'e}orie combinatoire de s{\'e}ries formelles}
\cite{J:combinatorial.species}, Joyal defines a combinatorial species to be a
functor $A$ from the groupoid of finite sets and bijections to the category of
sets, assigning every set $\underline{n}$ a set $A_n$ isovariantly. One
associates a series to a combinatorial species by taking the cardinality of the
$A_n$ and from there derive a generating function. But one can proceed in
another way by first making a \emph{generating functor}\footnote{In truth, one
  derives what is known as an \emph{analtyic} functor from this operation, and
  not a polynomial functor. This is because one must also quotient by the action
  of the symmetric groups on $A_n$. This difficulty is rectified when passing to
  homotopy types, where analytic functors are polynomial due to the better
  behavior of homotopy colimits.}
 $$X \mapsto \sum_{n \in \Nb} A_n \times X^n$$
from the category of sets to itself, and then taking the action of this functor
on cardinalities.

Such functors $\Set \to \Set$ are sums of representable functors, and are
therefore examples of \emph{polynomial functors}. Polynomial functors are well
studied objects with a beautiful theory. They are important in computer science
for the study of data types (cite), as a way of describing operads (cite), and
for the development of opetopic approaches to higher categories (cite). The
class of polynomial functors can be described in a number of equivalent ways:
\begin{thm}[cite something]
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is a sum of representables.
  \item $P$ is accessible and preserves connected limits.
  \item There is a bundle $\pi : E \to B$ of sets, and $P$ is the composite
    $$\Set \xto{E^{\ast}} \Set_{/E} \xto{\pi_{!}} \Set_{/B} \xto{B_{\ast}}.$$
  \item $P$ is a local right adjoint.
  \end{enumerate}
\end{thm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Second Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
(using depented type syntax) acting covariantly on rows and contravariantly on
boxes in each row. In terms of bundles, this is a diagram of the following sort:

>>>>

@@

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
(using dependent type syntax) acting covariantly on rows and contravariantly on
boxes in each row. In terms of bundles, this is a diagram of the following sort:
